---
title: "SRP-199"
author: "Celeste Vargas (305395537)"
date: "2023-03-15"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# I. Downloading and Cleaning Data
```{r}
data <- read.csv("C://SRP//AAP 2021-2022 Annual Survey, merged with membership data, deidentified.csv")
```

```{r}
#head(data)
#colnames(data)
#View(data)
library(haven)
library(tidyverse)
library(broom)
library(pander)
data <- read_sav("C://SRP//AAP 2021-2022 Annual Survey cleaned, merged with membership data, FTSP var, S22TermGPA, deidentified.sav")
View(data)
```
```{r}
dim(data)
```

```{r}
unique(data$majorName)

life_sci <- c("Psychobiology", "Pre Psychobiology", "Neuroscience",
              "Molecular, Cell, and Developmental Biology", 
              "Microbiology,Immunology&Molecular Genetics", "Marine Biology", "Biology", "Physiological Science"
              , "Human Biology and Society (BS)", "Cognitive Science", 
              "Pre Cognitive Science", "Ecology,Behavior,and Evolution", 
              "Environmental Science", "Pre Human Biology and Society (BS)",
              "Linguistics and Psychology", "Geography/Environmental Studies", 
              "Precomputational and Systems Biology", 
              "Computational and Systems Biology", 
              "Pre Human Biology and Society", "Psychology", "Pre Psychology")

phy_sci <- c("Applied Mathematics", "Pre Mathematics", "Pre-Data Theory", 
             "Mathematics of Computation", "Pre Mathematics/Economics", 
             "Biochemistry", "Mathematics for Teaching", 
             "Pre Mathematics/Economics", "Astrophysics", 
             "Statistics", "Chemistry", "Biophysics", 
             "Atmospheric and Oceanic Sciences", "Pre Statistics", 
             "Pre Applied Mathematics")
```

# II. Basic Stats of Data and Creation of Data Sets
```{r}
life_science <- data[data$majorName %in% life_sci,]

physical_science <- data[data$majorName %in% phy_sci,]

```

```{r}
write.csv(life_science, "life_sci.csv")
write.csv(physical_science, "phy_sci.csv")
```

```{r}
dim(life_science)
dim(physical_science)
```


#Finding n's
```{r}
one <- life_science %>% count(SelfDoubt_Re_Ability) %>% as_factor()
two <- life_science %>% count(SelfConfidence_in_Academics)
three <- life_science %>% count(Sense_of_Belonging)
seven <- life_science %>% count(AAP_21_22_utilize1)

four <- physical_science %>% count(SelfDoubt_Re_Ability)
five <- physical_science %>% count(SelfConfidence_in_Academics)
six <-  physical_science %>% count(Sense_of_Belonging)
eight <- physical_science %>% count(AAP_21_22_utilize1)


n_function <- function(n){
  
  last_number <- length(n$n)
  na <- n$n[last_number]
  
  the_sum <- sum(n$n[-last_number])
  
  my_data_frame <- data.frame(n = the_sum, na = na)
  
  my_data_frame
  
}

n_function(one)
n_function(two)
n_function(three)
n_function(seven)

n_function(four)
n_function(five)
n_function(six)
n_function(eight)

dim(life_science)
dim(physical_science)


```

```{r}
life_science %>% count(majorName) %>% as_factor()

physical_science %>% count(majorName) %>% as_factor()

life_science %>% count(degreeExpectedTerm) %>% as_factor()
physical_science %>% count(degreeExpectedTerm) %>% as_factor()

life_science %>% count(gender_recoded) %>% as_factor()
physical_science %>% count(gender_recoded)

life_science %>% count(gender) %>% as_factor()
physical_science %>% count(gender)  %>% as_factor()

life_science %>% count(academic_status) %>% as_factor()
physical_science %>% count(academic_status) %>% as_factor()

life_science %>% count(AAP_21_22_utilize1) %>% as_factor()
physical_science %>% count(AAP_21_22_utilize1) %>% as_factor()
```
```{r}
life_sci_lower <- life_science[life_science$degreeExpectedTerm %in% c("24S", "25S"),]
phy_sci_lower <- physical_science[physical_science$degreeExpectedTerm %in% c("24S", "25S"),]
```


```{r}
hist(life_science$SelfDoubt_Re_Ability)
hist(life_science$SelfConfidence_in_Academics)
hist((life_science$Sense_of_Belonging))

shapiro.test(life_science$SelfDoubt_Re_Ability)
shapiro.test(life_science$SelfConfidence_in_Academics)
shapiro.test((life_science$Sense_of_Belonging))



```
```{r}
hist(physical_science$SelfDoubt_Re_Ability)
hist(physical_science$SelfConfidence_in_Academics)
hist(physical_science$Sense_of_Belonging)

shapiro.test(physical_science$SelfDoubt_Re_Ability)
shapiro.test(physical_science$SelfConfidence_in_Academics)
shapiro.test(physical_science$Sense_of_Belonging)
```



```{r}
wilcox.test(life_science$SelfDoubt_Re_Ability, physical_science$SelfDoubt_Re_Ability)
wilcox.test(life_science$SelfConfidence_in_Academics, physical_science$SelfConfidence_in_Academics)
wilcox.test(life_science$Sense_of_Belonging, physical_science$Sense_of_Belonging)

# table1 <- tidy(t_test1)
# pander(t_test1)
# 
# table2 <- tidy(t_test2)
# pander(t_test2)
# 
# table3 <- tidy(t_test3)
# pander(t_test3)
```

```{r}
life_science %>%
  summarise(median = median(life_science$SelfConfidence_in_Academics, na.rm = TRUE),
            quantile = IQR(life_science$SelfConfidence_in_Academics, na.rm = TRUE))

life_science %>%
  summarise(median = median(life_science$SelfDoubt_Re_Ability, na.rm = TRUE),
            quantile = IQR(life_science$SelfDoubt_Re_Ability, na.rm = TRUE))
life_science %>%
  summarise(median = median(life_science$Sense_of_Belonging, na.rm = TRUE),
            quantile = IQR(life_science$Sense_of_Belonging, na.rm = TRUE))

physical_science %>%
  summarise(median = median(physical_science$SelfDoubt_Re_Ability, na.rm = TRUE),
            quantile = IQR(physical_science$SelfDoubt_Re_Ability, na.rm = TRUE))

physical_science %>%
  summarise(median = median(physical_science$SelfConfidence_in_Academics, na.rm = TRUE),
            quantile = IQR(physical_science$SelfConfidence_in_Academics, na.rm = TRUE))

physical_science %>%
  summarise(median = median(physical_science$Sense_of_Belonging, na.rm = TRUE),
            quantile = IQR(physical_science$Sense_of_Belonging, na.rm = TRUE))

#-----------------------------------------------------------------------------------------
fem_life_sci %>%
  summarise(median = median(fem_life_sci$SelfConfidence_in_Academics, na.rm = TRUE),
            quantile = IQR(fem_life_sci$SelfConfidence_in_Academics, na.rm = TRUE))

fem_life_sci %>%
  summarise(median = median(fem_life_sci$SelfDoubt_Re_Ability, na.rm = TRUE),
            quantile = IQR(fem_life_sci$SelfDoubt_Re_Ability, na.rm = TRUE))
fem_life_sci %>%
  summarise(median = median(fem_life_sci$Sense_of_Belonging, na.rm = TRUE),
            quantile = IQR(fem_life_sci$Sense_of_Belonging, na.rm = TRUE))


fem_phy_sci %>%
  summarise(median = median(fem_phy_sci$SelfConfidence_in_Academics, na.rm = TRUE),
            quantile = IQR(fem_phy_sci$SelfConfidence_in_Academics, na.rm = TRUE))

fem_phy_sci %>%
  summarise(median = median(fem_phy_sci$SelfDoubt_Re_Ability, na.rm = TRUE),
            quantile = IQR(fem_phy_sci$SelfDoubt_Re_Ability, na.rm = TRUE))
fem_phy_sci %>%
  summarise(median = median(fem_phy_sci$Sense_of_Belonging, na.rm = TRUE),
            quantile = IQR(fem_phy_sci$Sense_of_Belonging, na.rm = TRUE))


#------------------------------------------------------------------------------------

male_life_sci %>%
  summarise(median = median(male_life_sci$SelfConfidence_in_Academics, na.rm = TRUE),
            quantile = IQR(male_life_sci$SelfConfidence_in_Academics, na.rm = TRUE))

male_life_sci %>%
  summarise(median = median(male_life_sci$SelfDoubt_Re_Ability, na.rm = TRUE),
            quantile = IQR(male_life_sci$SelfDoubt_Re_Ability, na.rm = TRUE))
male_life_sci %>%
  summarise(median = median(male_life_sci$Sense_of_Belonging, na.rm = TRUE),
            quantile = IQR(male_life_sci$Sense_of_Belonging, na.rm = TRUE))

male_phy_sci %>%
  summarise(median = median(male_phy_sci$SelfConfidence_in_Academics, na.rm = TRUE),
            quantile = IQR(male_phy_sci$SelfConfidence_in_Academics, na.rm = TRUE))

male_phy_sci %>%
  summarise(median = median(male_phy_sci$SelfDoubt_Re_Ability, na.rm = TRUE),
            quantile = IQR(fem_phy_sci$SelfDoubt_Re_Ability, na.rm = TRUE))
male_phy_sci %>%
  summarise(median = median(male_phy_sci$Sense_of_Belonging, na.rm = TRUE),
            quantile = IQR(fem_phy_sci$Sense_of_Belonging, na.rm = TRUE))

```


```{r}
mean(physical_science$TermGPA, na.rm = TRUE)
mean(life_science$TermGPA, na.rm = TRUE)
```
```{r}
ggplot(life_science, aes(x = AAP_21_22_utilize1)) +
geom_bar(color = "blue", fill = "blue") +
  xlab("PLF Utiization Levels (N = 216)") +
  ylab("Count of PLF Utilization") +
  ggtitle("PLF Utilization - Life Sciences") 
ggplot(physical_science, aes(x = AAP_21_22_utilize1)) +
geom_bar(color = "lightblue", fill = "lightblue") +
  xlab("PLF Utilization Levels (N = 38)") +
  ylab("Count of PLF Utilization") +
  ggtitle("PLF Utilization - Physical Sciences") 
```


```{r}


life_lower <- life_sci_lower[life_sci_lower$academic_status == 1,]

phy_lower <- phy_sci_lower[phy_sci_lower$academic_status == 1,]

dim(life_lower)
dim(phy_lower)
```



```{r}
ggplot(life_lower, aes(x = AAP_21_22_utilize1)) +
geom_bar(color = "blue", fill = "blue") +
  xlab("PLF Utiization Levels (N = 108)") +
  ylab("Count of PLF Utilization") +
  ggtitle("PLF Utilization - Life Sciences (C/O 24S, 25S)") 

ggplot(phy_lower, aes(x = AAP_21_22_utilize1)) +
geom_bar(color = "lightblue", fill = "lightblue") +
  xlab("PLF Utilization Levels (N = 18)") +
  ylab("Count of PLF Utilization") +
  ggtitle("PLF Utilization - Physical Sciences (C/O 24S, 25S)") 
```





```{r}
plot(physical_science$Sense_of_Belonging, physical_science$TermGPA)
plot(life_science$Sense_of_Belonging, life_science$TermGPA)

plot(physical_science$SelfDoubt_Re_Ability, physical_science$TermGPA)
plot(life_science$SelfDoubt_Re_Ability, life_science$TermGPA)

plot(physical_science$SelfConfidence_in_Academics, physical_science$TermGPA)
plot(life_science$SelfConfidence_in_Academics, life_science$TermGPA)

```



```{r}
library(car)
```


```{r}
reg <- lm(physical_science$TermGPA ~ physical_science$Sense_of_Belonging + physical_science$SelfConfidence_in_Academics + physical_science$SelfDoubt_Re_Ability + physical_science$gender + physical_science$SelfEsteem_mean + physical_science$degreeExpectedTerm)

#summary(reg)
pander(reg)
avPlots(reg)
```


```{r}
reg2 <- lm(life_science$TermGPA ~ life_science$Sense_of_Belonging + life_science$SelfConfidence_in_Academics + life_science$SelfDoubt_Re_Ability + life_science$gender + life_science$SelfEsteem_mean + life_science$degreeExpectedTerm)

#summary(reg2)
pander(reg2)
avPlots(reg2)
```


## Females and Males
```{r}
fem_life_sci <- life_science[life_science$gender == 1,]
male_life_sci <- life_science[life_science$gender == 2,]

fem_phy_sci <- physical_science[physical_science$gender == 1,]
male_phy_sci <- physical_science[physical_science$gender == 2,]
```

```{r}
dim(fem_life_sci)
dim(male_life_sci)

dim(male_phy_sci)
dim(fem_phy_sci)
```



```{r}
shapiro.test(fem_life_sci$SelfDoubt_Re_Ability)
shapiro.test(male_life_sci$SelfDoubt_Re_Ability)

shapiro.test(fem_life_sci$SelfConfidence_in_Academics)
shapiro.test(male_life_sci$SelfConfidence_in_Academics)

shapiro.test(fem_life_sci$Sense_of_Belonging)
shapiro.test(male_life_sci$Sense_of_Belonging)
```

```{r}
hist(fem_life_sci$SelfDoubt_Re_Ability)
hist(male_life_sci$SelfDoubt_Re_Ability)

hist(fem_life_sci$SelfConfidence_in_Academics)
hist(male_life_sci$SelfConfidence_in_Academics)

hist(fem_life_sci$Sense_of_Belonging)
hist(male_life_sci$Sense_of_Belonging)

hist(fem_phy_sci$SelfDoubt_Re_Ability)
hist(male_phy_sci$SelfDoubt_Re_Ability)

hist(fem_phy_sci$SelfConfidence_in_Academics)
hist(male_phy_sci$SelfConfidence_in_Academics)

hist(fem_phy_sci$Sense_of_Belonging)
hist(male_phy_sci$Sense_of_Belonging)

shapiro.test(fem_phy_sci$SelfDoubt_Re_Ability)
shapiro.test(sqrt(male_phy_sci$SelfDoubt_Re_Ability))

shapiro.test(sqrt(fem_phy_sci$SelfConfidence_in_Academics))
shapiro.test(male_phy_sci$SelfConfidence_in_Academics)

shapiro.test(fem_phy_sci$Sense_of_Belonging)
shapiro.test(male_phy_sci$Sense_of_Belonging)

```

## t-test
```{r}
sd(fem_life_sci$SelfDoubt_Re_Ability, na.rm = TRUE)
sd(male_life_sci$SelfDoubt_Re_Ability, na.rm = TRUE)

sd(fem_life_sci$SelfConfidence_in_Academics, na.rm = TRUE)
sd(male_life_sci$SelfConfidence_in_Academics, na.rm = TRUE)


sd(fem_life_sci$Sense_of_Belonging, na.rm = TRUE)
sd(male_life_sci$Sense_of_Belonging, na.rm = TRUE)


sd(fem_phy_sci$SelfDoubt_Re_Ability, na.rm = TRUE)
sd(male_phy_sci$SelfDoubt_Re_Ability, na.rm = TRUE)

sd(fem_phy_sci$SelfConfidence_in_Academics, na.rm = TRUE)
sd(male_phy_sci$SelfConfidence_in_Academics, na.rm = TRUE)

sd(fem_phy_sci$Sense_of_Belonging, na.rm = TRUE)
sd(male_phy_sci$Sense_of_Belonging, na.rm = TRUE)


sd(life_science$SelfDoubt_Re_Ability, na.rm = TRUE)
sd(physical_science$SelfDoubt_Re_Ability, na.rm = TRUE)

sd(life_science$SelfConfidence_in_Academics, na.rm = TRUE)
sd(physical_science$SelfConfidence_in_Academics, na.rm = TRUE)

sd(life_science$Sense_of_Belonging, na.rm = TRUE)
sd(physical_science$Sense_of_Belonging, na.rm = TRUE)


wilcox.test(fem_life_sci$SelfDoubt_Re_Ability, male_life_sci$SelfDoubt_Re_Ability)
wilcox.test(fem_life_sci$SelfConfidence_in_Academics, male_life_sci$SelfConfidence_in_Academics)
wilcox.test(fem_life_sci$Sense_of_Belonging, male_life_sci$Sense_of_Belonging)

# table4 <- tidy(t_test4)
# pander(table4)
# 
# table5 <- tidy(t_test5)
# pander(table5)
# 
# table6 <- tidy(t_test6)
# pander(table6)
```


```{r}
wilcox.test(fem_phy_sci$SelfDoubt_Re_Ability, male_phy_sci$SelfDoubt_Re_Ability, exact = FALSE)
wilcox.test(fem_phy_sci$SelfConfidence_in_Academics, male_phy_sci$SelfConfidence_in_Academics)
wilcox.test(fem_phy_sci$Sense_of_Belonging, male_phy_sci$Sense_of_Belonging)

# table7 <- tidy(t_test7)
# pander(table7)
# table8 <- tidy(t_test8)
# pander(table8)
# table9 <- tidy(t_test9)
# pander(table9)
```


```{r}
wilcox.test(fem_life_sci$SelfDoubt_Re_Ability, fem_phy_sci$SelfDoubt_Re_Ability)
wilcox.test(fem_life_sci$SelfConfidence_in_Academics, fem_phy_sci$SelfConfidence_in_Academics)
wilcox.test(fem_life_sci$Sense_of_Belonging, fem_phy_sci$Sense_of_Belonging)

# table10 <- tidy(t_test10)
# pander(table10)
# 
# table11 <- tidy(t_test11)
# pander(table11)
# 
# table12 <- tidy(t_test12)
# pander(table12)
```

```{r}
wilcox.test(male_life_sci$SelfDoubt_Re_Ability, male_phy_sci$SelfDoubt_Re_Ability)
wilcox.test(male_life_sci$SelfConfidence_in_Academics, male_phy_sci$SelfConfidence_in_Academics)
wilcox.test(male_life_sci$Sense_of_Belonging, male_phy_sci$Sense_of_Belonging)

# table13 <- tidy(t_test13)
# pander(table13)
# 
# table14 <- tidy(t_test14)
# pander(table14)
# 
# table15 <- tidy(t_test15)
# pander(t_test15)
```



```{r}
library(ggpubr)

ggplot(life_science, aes(x = SelfDoubt_Re_Ability, y = TermGPA)) + 
  geom_point(size = 3, shape = 21, color = "black", fill = "blue") + 
  stat_cor(p.accuracy = 0.001, r.accuracy = 0.01, label.x.npc = "left",
  label.y.npc = "bottom")

ggplot(life_science, aes(x = SelfConfidence_in_Academics, y = TermGPA)) + 
  geom_point(size = 3, shape = 21, color = "black", fill = "blue") + 
  stat_cor(p.accuracy = 0.001, r.accuracy = 0.01,label.x.npc = "left",
  label.y.npc = "bottom")

ggplot(life_science, aes(x = Sense_of_Belonging, y = TermGPA)) + 
  geom_point(size = 3, shape = 21, color = "black", fill = "blue") + 
  stat_cor(p.accuracy = 0.001, r.accuracy = 0.01, label.x.npc = "left",
  label.y.npc = "bottom")
```


### Samples are very small for the physical science students, so it makes sense that the correlations are non significant.
```{r}
ggplot(physical_science, aes(x = SelfDoubt_Re_Ability, y = TermGPA)) + 
  geom_point(size = 3, shape = 21, color = "black", fill = "blue") + 
  stat_cor(p.accuracy = 0.001, r.accuracy = 0.01, label.x.npc = "left",
  label.y.npc = "bottom")

ggplot(physical_science, aes(x = SelfConfidence_in_Academics, y = TermGPA)) + 
  geom_point(size = 3, shape = 21, color = "black", fill = "blue") + 
  stat_cor(p.accuracy = 0.001, r.accuracy = 0.01,label.x.npc = "left",
  label.y.npc = "bottom")

ggplot(physical_science, aes(x = Sense_of_Belonging, y = TermGPA)) + 
  geom_point(size = 3, shape = 21, color = "black", fill = "blue") + 
  stat_cor(p.accuracy = 0.001, r.accuracy = 0.01, label.x.npc = "left",
  label.y.npc = "bottom")
```
### MEAN PLOTS

### FEM LIFE SCI 
```{r}
ggplot(fem_life_sci, aes(x = SelfConfidence_in_Academics, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "blue") +
  stat_summary(fun.y = mean)+
  labs(y="Female", x = "Self Confidence in Academics")
 # geom_bar(data = fem_phy_sci, aes(x = mean(SelfDoubt_Re_Ability)), fun.y = "mean", na.rm = TRUE)
```
```{r}
ggplot(fem_life_sci, aes(x = SelfDoubt_Re_Ability, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "blue") +
  stat_summary(fun.y = mean)+
  labs(y="Female", x = "Self Doubt in Academics")

```
```{r}
ggplot(fem_life_sci, aes(x = Sense_of_Belonging, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "blue") +
  stat_summary(fun.y = mean) +
  labs(y="Female", x = "Sense of Belonging")
```

### fem physical science
```{r}
ggplot(fem_phy_sci, aes(x = SelfDoubt_Re_Ability, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "light blue") +
  stat_summary(fun.y = mean)+
  labs(y="Female", x = "Self Doubt in Academics")
```

```{r}
ggplot(fem_phy_sci, aes(x = SelfConfidence_in_Academics, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "light blue") +
  stat_summary(fun.y = mean) +
  labs(y="Female", x = "Self Confidence in Academics")
```

```{r}
ggplot(fem_phy_sci, aes(x = Sense_of_Belonging, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "light blue") +
  stat_summary(fun.y = mean) +
  labs(y="Female", x = "Sense of Belonging")
```



### male life sci
```{r}
ggplot(male_life_sci, aes(x = SelfDoubt_Re_Ability, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "blue") +
  stat_summary(fun.y = mean) +
  labs(y="Male", x = "Self Doubt in Academics")
```

```{r}
ggplot(male_life_sci, aes(x = SelfConfidence_in_Academics, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "blue") +
  stat_summary(fun.y = mean) +
  labs(y="Male", x = "Self Confidence in Academics")
```

```{r}
ggplot(male_life_sci, aes(x = Sense_of_Belonging, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "blue") +
  stat_summary(fun.y = mean) +
  labs(y="Male", x = "Sense of Belonging")
```
### male phy sci
```{r}
ggplot(male_phy_sci, aes(x = SelfDoubt_Re_Ability, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "light blue") +
  stat_summary(fun.y = mean) +
  labs(y="Male", x = "Self Doubt in Academics")
```

```{r}
ggplot(male_phy_sci, aes(x = SelfConfidence_in_Academics, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "light blue") +
  stat_summary(fun.y = mean) +
  labs(y="Male", x = "Self Confidence in Academics")
```

```{r}
ggplot(male_phy_sci, aes(x = Sense_of_Belonging, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "light blue") +
  stat_summary(fun.y = mean) +
  labs(y="Male", x = "Sense of Belonging")
```


### life sci
```{r}
ggplot(life_science, aes(x = SelfDoubt_Re_Ability, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "blue") +
  stat_summary(fun.y = mean) +
  labs(y="Life Science", x = "Self Doubt in Academics")
```
```{r}
ggplot(life_science, aes(x = SelfConfidence_in_Academics, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "blue") +
  stat_summary(fun.y = mean) +
  labs(y="Life Science", x = "Self Confidence in Academics")
```

```{r}
ggplot(life_science, aes(x = Sense_of_Belonging, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "blue") +
  stat_summary(fun.y = mean) +
  labs(y="Life Science", x = "Sense of Belonging")
```


### physical sci
```{r}
ggplot(physical_science, aes(x = SelfDoubt_Re_Ability, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "light blue") +
  stat_summary(fun.y = mean) +
  labs(y="Physical Science", x = "Self Doubt in Academics")
```

```{r}
ggplot(physical_science, aes(x = SelfConfidence_in_Academics, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "light blue") +
  stat_summary(fun.y = mean) +
  labs(y="Physical Science", x = "Self Confidence in Academics")
```

```{r}
ggplot(physical_science, aes(x = Sense_of_Belonging, y = factor(0))) +
  geom_boxplot(alpha = 0.7, fill = "light blue") +
  stat_summary(fun.y = mean) +
  labs(y="Physical Science", x = "Sense of Belonging")
```


### physical sci male vs fem
```{r}
ggplot(physical_science, aes( x = factor(gender), y = SelfDoubt_Re_Ability)) +
  geom_boxplot(alpha = 0.7, fill = "light blue") +
  stat_summary(fun.y = mean) +
  labs(y="Self Doubt in Academics", x = "Gender")
```
```{r}
ggplot(physical_science, aes( x = factor(gender), y = SelfConfidence_in_Academics)) +
  geom_boxplot(alpha = 0.7, fill = "light blue") +
  stat_summary(fun.y = mean) +
  labs(y="Self Confidence in Academics", x = "Gender")
```

```{r}
ggplot(physical_science, aes( x = factor(gender), y = Sense_of_Belonging)) +
  geom_boxplot(alpha = 0.7, fill = "light blue") +
  stat_summary(fun.y = mean) +
  labs(y="Sense of Belonging", x = "Gender")
```


#life sci male vs fem
```{r}
ggplot(life_science, aes( x = factor(gender), y = SelfDoubt_Re_Ability)) +
  geom_boxplot(alpha = 0.7, fill = "blue") +
  stat_summary(fun.y = mean) +
  labs(y="Self Doubt in Academics", x = "Gender")
```
```{r}
ggplot(life_science, aes( x = factor(gender), y = SelfConfidence_in_Academics)) +
  geom_boxplot(alpha = 0.7, fill = "blue") +
  stat_summary(fun.y = mean) +
  labs(y="Self Confidence in Academics", x = "Gender")
```

```{r}
ggplot(life_science, aes( x = factor(gender), y = Sense_of_Belonging)) +
  geom_boxplot(alpha = 0.7, fill = "blue") +
  stat_summary(fun.y = mean) +
  labs(y="Sense of Belonging", x = "Gender")
```

```{r}
fem1 <- fem_life_sci %>% count(SelfDoubt_Re_Ability) %>% as_factor()
fem2 <- fem_life_sci %>% count(SelfConfidence_in_Academics)
fem3 <- fem_life_sci %>% count(Sense_of_Belonging)

n_function(fem1)
n_function(fem2)
n_function(fem3)

fem4 <- fem_phy_sci %>% count(SelfDoubt_Re_Ability) %>% as_factor()
fem5 <- fem_phy_sci %>% count(SelfConfidence_in_Academics)
fem6 <- fem_phy_sci %>% count(Sense_of_Belonging)

n_function(fem4)
n_function(fem5)
n_function(fem6)

```



```{r}
m1 <- male_life_sci %>% count(SelfDoubt_Re_Ability) %>% as_factor()
m2 <- male_life_sci %>% count(SelfConfidence_in_Academics)
m3 <- male_life_sci %>% count(Sense_of_Belonging)

n_function(m1)
n_function(m2)
n_function(m3)

m4 <- male_phy_sci %>% count(SelfDoubt_Re_Ability) %>% as_factor()
m5 <- male_phy_sci %>% count(SelfConfidence_in_Academics)
m6 <- male_phy_sci %>% count(Sense_of_Belonging)

n_function(m4)
n_function(m5)
n_function(m6)
```

```{r}
chisq.test(life_science$SelfDoubt_Re_Ability, physical_science$SelfDoubt_Re_Ability)
```

